Dipolar interactions in dense ensembles of Nitrogen-Vacancy centers

### 2022-05-19 Talks/Journées de l'axe/presentation.tex
tata

\begin{document}
\begin{frame}
\maketitle
\centering
\includegraphics[scale=.2]{Nitrogen-vacancy_center}
\end{frame}
%\begin{frame}{Outline}
%\tableofcontents
%\end{frame}
%\section{Physics of the NV center}
\begin{frame}{Team main activities}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide activités}
\end{frame}

\begin{frame}{Optical properties of NV$^-$ centers}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_NV_optical}
\end{frame}
%\begin{frame}{NV$^-$ center electronic structure}
%\centering
%\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{NV_8_niveaux_1}
%\end{frame}
%\begin{frame}{NV$^-$ center electronic structure}
%\centering
%\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{NV_8_niveaux_2}
%\end{frame}
\begin{frame}{NV$^-$ center electronic structure}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{NV_8_niveaux_3}
\end{frame}
\begin{frame}{NV center spin sub-levels}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_3_niveaux}
\end{frame}
\begin{frame}{Optically Detected Magnetic Resonance (ODMR)}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide ODMR}
\end{frame}
\begin{frame}{Modification of the spin $T_1$ with dense ensemble}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_T1_1}
\end{frame}
\begin{frame}{Modification of the spin $T_1$ due to resonant dipole coupling}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_T1_2}
\end{frame}
\begin{frame}{Dipole-dipole coupling in zero magnetic field}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide zero field}
\end{frame}
\begin{frame}{Conclusion}
\begin{itemize}
\item The NV$^-$ center is an optically active defect in diamond which allows an optical control and readout of its spin state.
\bigskip
\item The depolarization of the spins is modified in dense ensemble due to dipole-dipole coupling.
\bigskip
\item This effect is even stronger in zero-magnetic field.
\end{itemize}
\end{frame}
\begin{frame}{Bonus : Magnetometry in zero magnetic field}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_magneto}
\end{frame}

\end{document}

>>>>

\begin{document}
\begin{frame}
\maketitle
\centering
\includegraphics[scale=.2]{Nitrogen-vacancy_center}
\end{frame}
%\begin{frame}{Outline}
%\tableofcontents
%\end{frame}
%\section{Physics of the NV center}
\begin{frame}{What are NV centers ?}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide  NV properties}
\end{frame}
\begin{frame}{Common example : Optically Detected Magnetic Resonance (ODMR)}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide ODMR}
\end{frame}

\begin{frame}{What are NV centers and why are they everywhere ?}
\begin{itemize}
\item Good optical properties : quantum yield $\approx 1$, stable in time and temperature
\medskip
\item Good spin properties : $T_1\approx\ \rm ms$ and $T_2^*\sim \mu$s at 300 K.
\medskip
\item Optical polarization (up to 90\%) and readout (fidelity up to 0.3) of the spin at room temperature
\end{itemize}
\bigskip
$\to$ One of the most versatile spin qubit at room temperature
\end{frame}

\begin{frame}{What are NV centers being used for ?}
$\bullet$ Quantum memories :
\begin{center}
\includegraphics[width=0.8\textwidth,height=0.9\textheight,keepaspectratio]{mémoire}
\end{center}

$\bullet$ Intrication :
\begin{center}
\includegraphics[width=0.8\textwidth,height=0.9\textheight,keepaspectratio]{Intrication}
\end{center}
\end{frame}

\begin{frame}{Magnetomtry with NV centers : big or small}
$\bullet$ AFM nano-scale magnetomtry :
\begin{center}
\includegraphics[width=0.65\textwidth,height=0.9\textheight,keepaspectratio]{magneto AFM}
\end{center}

$\bullet$ Diamond magnetic microscopy :
\begin{center}
\includegraphics[width=0.65\textwidth,height=0.9\textheight,keepaspectratio]{magneto graphene}
\end{center}
\end{frame}

\begin{frame}{Context of my PhD work : new physics with dense ensemble of NV centers}
\begin{itemize}
\item To increase the ensemble sensitivity we need to increase the density of NV centers
\item Chemists and material scientists have made huge progress to grow NV-rich diamond with little other impurities 
\begin{center}
\includegraphics[width=0.65\textwidth,height=0.9\textheight,keepaspectratio]{diamant Alex}
\end{center}
\item When the defects density reaches a critical point, many body effects start to appear due to dipole-dipole interaction and charge tunneling (3 ppm of NV = 30 kHz dipole coupling between NV neighbors)
\end{itemize}
\end{frame}

\begin{frame}{Modification of the spin $T_1$ due to resonant dipole coupling}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_T1_2}
\end{frame}
\begin{frame}{Conclusion}
Acknowledgments : Christine et les autres

\bigskip
Take home messages : 
\begin{itemize}
\item NV centers are defects in diamond with an optically controllable and readable spin at room temperature
\medskip
\item Many body effects start to manifest with the new NV-rich samples being made
\end{itemize}
\end{frame}
\begin{frame}{Bonus : Magnetometry in zero magnetic field}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{Slide_magneto}
\end{frame}
\begin{frame}{Optical properties of NV$^-$ centers}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_NV_optical}
\end{frame}
\begin{frame}{NV$^-$ center electronic structure}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{NV_8_niveaux_3}
\end{frame}
\begin{frame}{NV center spin sub-levels}
\centering
\includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{slide_3_niveaux}
\end{frame}
\end{document}
